---
title: "Lab 8"
author: "SSalem"
date: "3/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load packages
```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)


```

###Column graph of Texas oil Spills

```{r}
oil_spills<- read_csv("oil_spills.csv")


#allows you to filter what data you need from full df
df <- oil_spills %>% 
  filter(`Accident State` == "TX" & `Accident Year` < 2017)  %>% 
group_by(`Accident Year`) %>% 
  summarise(Loss = sum(`Net Loss (Barrels)`))

colnames(df)<- c("Year", "Loss")

ggplot(df, aes( x = Year, y = Loss))+
geom_col()


```


### Leaflet plot of spill locations in TX in 2016

```{r}
df_loc<- oil_spills %>% 
  filter(`Accident State`== "TX" & `Accident Year` == 2016) %>% 
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc) <- c("latitude", "longitude", "net_loss")

# recognizes it as spatial data
oil_sf <- st_as_sf(df_loc, coords = c("longitude", "latitude"), crs = 4326)
  
leaflet(oil_sf) %>% 
  addTiles() %>% 
  addMarkers()

# interactive map 
  
  
```
 ### tmap plot with the Texas state shapefile
 
```{r}

states <- st_read(dsn = ".", layer = "states") # can treate information as a data frame and will keep geometry of state lines

tex_boarder <- states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326)

plot(tex_boarder)


tm_shape(tex_boarder) +
  tm_polygons() +
  tm_shape(oil_sf) +
  tm_dots(size = 0.3)

```
 
### convert data to spatial points patterns (combination of point data and the bounding window)
must convert into point patter data 


```{r}

spill_sp <- as(oil_sf, "Spatial")
spill_ppp <- as(spill_sp, "ppp")

tx_sp <- as(tex_boarder, "Spatial")
tx_owin <- as(tx_sp, "owin") # r is recognizing this as window

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)

# last 4 functions taken spatial information and put it in language that understands (as point data)



```
### A denisty plot:
```{r}
plot(density(all_ppp, sigma = 0.4)) # be causious they are easy to make - can change the based on level of sigma

```

### Quadrat test for spatial evenness

```{r}
oil_qt <-quadrat.test(all_ppp, nx = 5, ny = 5)
oil_qt

plot(all_ppp)

plot(oil_qt, add = TRUE, cex = 0.4)
```

### G - Function for nearest neighbor analysis

```{r}
r <- seq(0,1, by = 0.01)


oil_gfun<-envelope(all_ppp, fun = Gest, r = r, nsim = 100)

ggplot(oil_gfun, aes(x = r, y = obs)) +
  geom_line(color = "black") +
  geom_line(aes(x = r, y = theo), color = "red")
# our observeddata has a higher porportion of point pares with nearest neighbors at shorter distance when compared to CSR data 
# model value of CSR 



```
## Nearest Neighbor using L function (Ripleys K Standardized)

```{r}
r2 <- seq(0, 3, by = 0.5)

oil_lfun<- envelope(all_ppp, fun = Lest, r = r2, nsim = 20, global = TRUE)
# radius simulation

ggplot(oil_lfun, aes(x = r2, y = obs)) +
  geom_line(color = "black") +
  geom_line(aes(x = r, y = theo), color = "red")
```

